---
title: "Multi-caRamel optimization with MPI"
author: "Fabrice Zaoui"
date: "March 02 2021"
output: html_document
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Pareto front of fronts with MPI}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(python.reticulate = FALSE)
```
## Short Description

**caRamel** is a multiobjective evolutionary algorithm combining the MEAS algorithm and the NGSA-II algorithm.

Download the package from CRAN or [GitHub](https://github.com/fzao/caRamel) and then install and load it.

```{r caRa, eval=F, echo=T}
library(caRamel)
```

This example will use the **pbdMPI** package in order to use several processes of caRamel. Download the package from CRAN and then install and load it. Make also sure that you have an MPI distribution installed on your system, see for instance [*Open MPI*](https://www.open-mpi.org) if necessary.

```{r pbdMPI, eval=F, echo=T}
library(pbdMPI)
```

[*Kursawe*](https://en.wikipedia.org/wiki/File:Kursawe_function.pdf) test function has two objectives of three variables.

```{python kursawe, eval=F, echo=T}
kursawe <- function(i) {
  k1 <- -10 * exp(-0.2 * sqrt(x[i,1]^2 + x[i,2]^2)) - 10 * exp(-0.2 * sqrt(x[i,2]^2 + x[i,3]^2))
  k2 <- abs(x[i,1])^0.8 + 5 * sin(x[i,1]^3) + abs(x[i,2])^0.8 + 5 * sin(x[i,2]^3) + abs(x[i,3])^0.8 + 5 * sin(x[i,3]^3)
  return(c(k1, k2))
}
```

The variables lie in the range [-5, 5]:

```{r kursawe_variable, eval=F, echo=T}
nvar <- 3 # number of variables
bounds <- matrix(data = 1, nrow = nvar, ncol = 2) # upper and lower bounds
bounds[, 1] <- -5 * bounds[, 1]
bounds[, 2] <- 5 * bounds[, 2]
```

Both functions are to be minimized:

```{r kursawe_objectives, eval=F, echo=T}
nobj <- 2 # number of objectives
minmax <- c(FALSE, FALSE) # min and min
```

Set algorithmic parameters and launch **caRamel**:

```{r kursawe_param, , eval=F, echo=T, fig.show="hide", results="hide"}
popsize <- 100 # size of the genetic population
archsize <- 100 # size of the archive for the Pareto front
maxrun <- 1000 # maximum number of calls
prec <- matrix(1.e-3, nrow = 1, ncol = nobj) # accuracy for the convergence phase

results <- 
  caRamel(nobj,
          nvar,
          minmax,
          bounds,
          wrapperFunction, # It's the wrapper function that will be called
          popsize,
          archsize,
          maxrun,
          prec)
```


